Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-11-29 contents/draft.tex
* \subsection{Motivation and Background} 제목만 제거 * \section{Re-ranking Model} 뒷부분과 \section{Experimental Results} 앞부분 내용 보완!

    \subsection{Motivation and Background}\label{subsec:motivation-and-background}

@@

@@

>>>>

@@

    In summary, the re-ranking model represents a significant advancement in our approach to Korean morphological analysis.
    By leveraging BERT-based models, we anticipate a marked improvement in accuracy, especially in complex linguistic scenarios.
    The next section will present our experimental setup and results, providing crucial empirical evidence for the efficacy of the re-ranking model in practical applications.

@@

    Having developed the re-ranking model as a theoretical framework for enhancing Korean morphological analysis, we now turn to empirical validation.
    This section outlines our experimental setup, designed meticulously to test the performance of our model.
    Through these experiments, we aim to demonstrate not just the model's accuracy but also its practical applicability in handling the nuances of Korean language processing.
